Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-06-09 Journal/JAS Data Association/JAS_DataAssoc (Taeyoung Lee's conflicted copy 2015-12-10).tex
journal added

%The Gaussian states are tracked with measurements; however, 
We consider the problem of estimating object states, when the number of objects for tracking is assumed known, but the measurement origins are unknown.
We assume that a sensor generates measurements, composed of only object detections and spurious readings from clutter.
Multiple measurements may originate from a single object, or an object may be missed entirely.
However, we assume that a single measurement does not originate from more than one object.
%We assume accurate measurement resolution, such that at maximum one measurement may originate from a single object, where this measurement is independent of other objects detected by the same sensor.
%Suppose that these measurements are not associated with a specific object, and they possibly include spurious measurements or missed detections, where the probability of detecting objects is assumed known. 
Data association and filtering serves to estimate the state of the systems when there exist uncertainties in the system processes, measurements, and measurement origins. In this paper, the popular joint probabilistic data association filtering is improved in two distinct ways in the subsequent sections.

@@

Let $G_{ij}\in\Re$ be a scaled density function used repeatedly between the $i$-th measurement estimate and the $j$-th measurement, defined as
% variable which takes a very similar form as the Gaussian probability density function
\begin{align}
G_{ij}=\frac1{\sqrt{\det{S_{i}}}}\exp{\{-\frac12e_{ij}^TS_{i}^{-1}e_{ij}\}}.
\end{align}
%This is used to calculate intermediate variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$
%\begin{align}
%\mathcal{S}_{ti}=\sum\limits_{j\in J}G_{ij}, 
%\quad 
%\mathcal{S}_{ri}=\sum\limits_{i\in I}G_{ij}.
%\end{align}
Then, a close approximation of the probability that the $i$-th system is associated with the $j$-th measurement is (from~\cite{Bar1990})
\begin{align}
\label{eqn:betaDef}
\beta_{ij}=\frac{G_{ij}}{\sum\limits_{l=1}^{n_r}G_{il}+\sum\limits_{l=1}^{n_t}G_{lj}-G_{ij}+B},
\end{align}
where $B$ accounts for measurements \emph{not} originating from known targets. When $B=0$, this corresponds to rare extraneous measurements and missed detections. When these are prevalent, tuning $B$ is required, though this is beyond the paper scope.

%When these are prevalent, a fixed value of $B$ in \refeqn{betaDef} was found from simulations to provide a close approximation of $\beta_{ij}$ in various applications, though tuning this parameter is beyond the scope of this paper.

@@

\begin{figure}
\setlength{\unitlength}{0.06\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.48\columnwidth]{CT.png}}
\put(5.3,1.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.6){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.2,5.2){\shortstack[c]{Weighted sum:\\ $\mathbf{J}=J_P+cJ_S$}}
%\put(4.98,0.78){\circle*{0.1}}
%\put(2.48,1.57){\circle*{0.1}}
%\put(5.00,0.81){\circle*{0.1}}
%\put(2.47,1.60){\circle*{0.1}}
\put(4.99,0.81){\circle*{0.1}}
\put(2.47,1.60){\circle*{0.1}}
\put(4.8,-0.4){$K_\text{M-JPDAF}$}
\put(2.3,-0.4){$K_\text{C-JPDAF}$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to an element of an estimator gain $K$ (blue dashed: uncertainty cost $J_P$, red dashed-dotted: similarity cost $J_S$, black solid: weighted sum). The estimator gain $K_\text{M-JPDAF}$ is selected to minimize the uncertainty cost. The estimator gain $K_\text{C-JPDAF}$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association during close proximity tracking scenarios or missions.}
\label{fig:CostTrends}
\end{figure}

@@

%For each following scenario, several cases are simulated where various parameters are slightly changed with $\epsilon\in\Re$, summarized in Table \ref{tab:CaseDef}, and measurement are simulated with \refeqn{NonLin2BP} and \refeqn{zj}.
In the following scenarios, several cases are simulated with \refeqn{NonLin2BP} and measurements are generated according to \refeqn{zj}, but the measurement origins are not given to the data association algorithm.
Additionally, there is a $10\%$ chance that a measurement is either deleted or an extraneous measurement is added at each time step.
Since this probability is relatively small, the association probabilities are computed with \refeqn{betaDef} using $B=0$.
Further descriptions of the cases are available below, and the resulting accuracy over $n$ time steps is measured with RMS position (kilometers) and angular (radian) errors, defined as
\begin{align}
% MATLAB: RMS_r_indiv(k) = (sum((Ri{k}-Rhati{k}).^2)/NumStates).^0.5;
\mathbf{e}_{RMS,r,i}=\sqrt{\frac{\sum_{k=1}^n\norm{r_{i,k}-\hat r_{i,k}}^2}{n}}
, \quad
\mathbf{e}_{RMS,\theta,i}=\sqrt{\frac{\sum_{k=1}^n(\cos^{-1}(r_{i,k}^T\hat r_{i,k}))^2}{n}}
,
\end{align}
respectively, and the subsequent tabulated RMS errors are averaged over all objects. The uncertainty is summarized with $\tr{J_P}$, and the computation time is measured as well, tabulated in Tables \ref{tab:I}--\ref{tab:IV}.
Scenarios I and II are data association and filtering examples in LEO, while scenarios III and IV are GEO examples.
For readers with interest in how the algorithms handle perturbations, various parameters are slightly changed, tabulated at each scenario description.
The metrics from the perturbed cases are summarized in the subsequent tables as well.

@@

Various cases in LEO are simulated to compare the data association and filtering algorithms, namely the JPDAF, M-JPDAF, and C-JPDAF.
The process covariance is $Q=\diag[\sigma^2_rI_{3\times3},\dot\sigma^2_rI_{3\times3}]=\diag[10^{-6}I_{3\times3}\ \text{km}^2, 10^{-8}I_{3\times3}\ (\text{km/s})^2]$ and the measurement uncertainty is $R=\diag[\sigma_\rho^2, \sigma_{\dot\rho}^2, \sigma_\alpha^2, \sigma_\delta^2]=\diag[(0.15\ \text{km})^2, (0.005\ \text{km/s})^2,\\ (\frac{0.01\pi}{180}\ \text{rad})^2, (\frac{0.01\pi}{180}\ \text{rad})^2]\in\Re^{4\times4}$ where these standard deviations are selected from the Mahe Ground Station uncertainty data~\cite{VerSauSco04} and~\cite{KurAriAriEfe10}.

@@

These cases serve to compare the JPDAF with the M-JPDAF for tracking two nearby satellites passing over the sensor field of view in GEO, where the orbital radius is $r_\text{GEO}=4.2164\times10^{4}\ \text{km}$. The initial conditions of the first two orbits are chosen as
\begin{align*}
x_{1,\text{III}}&=\begin{bmatrix}r_{GEO}, & 0\ \text{km}, & 0\ \text{km}, & 0\ \text{km/s}, & \sqrt{\frac{\mu}{r_{GEO}}}, & 0\ \text{km/s}\end{bmatrix}^T,
\\
x_{2,\text{III}}&=x_{1,\text{III}}+\begin{bmatrix}
0\ \text{km}, & 0\ \text{km}, & -1\ \text{km}, & 0\ \text{km/s}, & 0\ \text{km/s}, & 4\times10^{-4}\ \text{km/s}
\end{bmatrix}^T,
\end{align*}
or where $x_{1,\text{III}}$ remains exactly in GEO while $x_{2,\text{III}}$ starts slightly perturbed from a GEO orbit with a nonzero inclination such that the two satellites nearly collide as they pass by in close proximity.
The perturbations are summarized in Table \ref{tab:PertCaseIII}.
\begin{table}
\begin{center}
\caption{Perturbations for Scenario III Cases} \label{tab:PertCaseIII}
\begin{threeparttable}[h]
\begin{tabularx}{.75\textwidth}
{
>{$}c<{$} |
>{$}c<{$}
}
\toprule
\multirow{2}{*}{Perturbed Case} & \multirow{2}{*}{Perturbation}\\
\\
\midrule
\multirow{1}{*}{III.a} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-6}\text{ km}^2$}
\\
\multirow{1}{*}{III.b} &  \multirow{1}{*}{$\sigma^2_{\dot r} = 1.1\times10^{-8}(\text{ km/s})^2$}
\\
\multirow{1}{*}{III.c} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-6}\text{ km}^2$, $\sigma^2_{\dot r} = 1.1\times10^{-8}(\text{ km/s})^2$}
\\
\multirow{1}{*}{III.d} &  \multirow{1}{*}{$\sigma^2_{\alpha} = \sigma^2_{\delta} = 3.3508\times10^{-8}\text{ rad}^2$}
\\
\bottomrule
\end{tabularx}
\end{threeparttable}
\end{center}
\end{table}
The III cases consider small initial covariance matrices $P_{0,\text{III}}= Q$ where $Q$ is defined the same as the LEO cases for time steps of $10$ seconds over $5000$ seconds.
%These scenarios are chosen because the estimates exhibit large initial uncertainties, so the spread in the innovations affects the updates.
Even though the initial conditions are largely different from those of the I cases, the III cases display the same trends, where the computational costs among the algorithms are roughly the same but the tracking abilities of the M-JPDAF \emph{always} yield estimates closer to the truth with less uncertainty than those of the JPDAF.
These results are tabulated in Table \ref{tab:III}, and some cases are plotted in Figure \ref{fig:III}.

@@

The JPDAF, M-JPDAF, and C-JPDAF algorithms are compared for two satellites in GEO with initial conditions
\begin{align}
\begin{split}
x_{1,\text{IV}}&=f_\text{GEO}(0^\circ), \quad x_{2,\text{IV}}=f_\text{GEO}({10^{-4}}^\circ), \quad \mbox{where}
\\
f_\text{GEO}(\theta)&=r_\text{GEO}\begin{bmatrix}\cos\theta, & \sin\theta, & 0, & -\sqrt{\frac{\mu}{r_\text{GEO}^3}}\sin\theta, & \sqrt{\frac{\mu}{r_\text{GEO}^3}}\cos\theta, & 0\end{bmatrix}^T,
\end{split}
\end{align}
where $Q=\diag[\sigma^2_rI_{3\times3}, \dot\sigma^2_rI_{3\times3}]=\diag[10^{-8}I_{3\times3}\ \text{km}^2, 10^{-10}I_{3\times3}\ \text{km/s}^2]$.
The perturbations are summarized in Table \ref{tab:PertCaseIV}.
\begin{table}
\begin{center}
\caption{Perturbations for Scenario IV Cases} \label{tab:PertCaseIV}
\begin{threeparttable}[h]
\begin{tabularx}{.75\textwidth}
{
>{$}c<{$} |
>{$}c<{$}
}
\toprule
\multirow{2}{*}{Perturbed Case} & \multirow{2}{*}{Perturbation}\\
\\
\midrule
\multirow{1}{*}{IV.a} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-8}\text{ km}^2$}
\\
\multirow{1}{*}{IV.b} &  \multirow{1}{*}{$\sigma^2_{\dot r} = 1.1\times10^{-10}(\text{ km/s})^2$}
\\
\multirow{1}{*}{IV.c} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-6}\text{ km}^2$, $\sigma^2_{\dot r} = 1.1\times10^{-8}(\text{ km/s})^2$}
\\
\multirow{1}{*}{IV.d} &  \multirow{1}{*}{$\sigma^2_{\alpha} = \sigma^2_{\delta} = 3.3508\times10^{-8}\text{ rad}^2$}
\\
\bottomrule
\end{tabularx}
\end{threeparttable}
\end{center}
\end{table}
The initial state covariance is $P_{0,\text{IV}}=Q$, where the time steps are $10$ seconds over a $2000$ second time period.
This corresponds to a scenario where two satellites orbit steadily nearby in GEO.
For the C-JPDAF, the parameters $a=1.5\times10^{2}$ and $c=1\times10^{10}$ from \refeqn{zetaGeneral} and \refeqn{CostGen} are used in these scenarios from trial and error.
In theory, topocentric right ascension measurements should be the same distance apart throughout the cases and the declination should always be zero.
Much like the II cases, the accuracy of the C-JPDAF yields a large improvement from that of the JPDAF and M-JPDAF; however, the increase in computational cost of the C-JPDAF is roughly $30$ times that of either other algorithm, which is about half of the increase found with the II cases.
This is because the similarity measure is less complex with the IV cases than with the II cases due to the number of estimates and the size of the measurement space.
The angular RMS errors and computation times are tabulated in Table \ref{tab:IV} and some example plots from these cases are shown in Figure \ref{fig:IV}. In applications with a large number of objects to track, the C-JPDAF need not be applied on most objects; only those close neighbors where the similarity among the estimates yield coalescence with the JPDAF or the M-JPDAF. This way, a data association scheme with an analytic solution, such as the JPDAF or the M-JPDAF, could be applied to the remaining estimates to mitigate the large computational requirements of the C-JPDAF.

>>>>

%The Gaussian states are tracked with measurements; however, 
We consider the problem of estimating object states, when the number of objects for tracking is assumed known, but the measurement origins are unknown. More explicitly, a measurement may be originated from a single object or it corresponds to spurious readings from clutter. Therefore, multiple measurements may originate from a single object, or an object may be missed entirely.
However, we assume that a single measurement does not originate from more than one object.
%We assume accurate measurement resolution, such that at maximum one measurement may originate from a single object, where this measurement is independent of other objects detected by the same sensor.
%Suppose that these measurements are not associated with a specific object, and they possibly include spurious measurements or missed detections, where the probability of detecting objects is assumed known. 
Data association and filtering serves to estimate the state of the systems when there exist uncertainties in the system processes, measurements, and measurement origins. In this paper, the popular joint probabilistic data association filtering is improved in two distinct ways in the subsequent sections.

@@

Let $G_{ij}\in\Re$ be a scaled density function used repeatedly between the $i$-th measurement estimate and the $j$-th measurement, defined as
% variable which takes a very similar form as the Gaussian probability density function
\begin{align}
G_{ij}=\frac1{\sqrt{\det{S_{i}}}}\exp{\{-\frac12e_{ij}^TS_{i}^{-1}e_{ij}\}}.
\end{align}
%This is used to calculate intermediate variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$
%\begin{align}
%\mathcal{S}_{ti}=\sum\limits_{j\in J}G_{ij}, 
%\quad 
%\mathcal{S}_{ri}=\sum\limits_{i\in I}G_{ij}.
%\end{align}
Then, a close approximation of the probability that the $i$-th system is associated with the $j$-th measurement is
\begin{align}
\label{eqn:betaDef}
\beta_{ij}=\frac{G_{ij}}{\sum\limits_{l=1}^{n_r}G_{il}+\sum\limits_{l=1}^{n_t}G_{lj}-G_{ij}+B},
\end{align}
where $B=0$ corresponds to rare extraneous measurements and missed detections. When these are prevalent, a fixed value of $B$ in \refeqn{betaDef} was found from simulations to provide a close approximation of $\beta_{ij}$ in various applications~\cite{Bar1990}.

@@

\begin{figure}
\setlength{\unitlength}{0.06\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.48\columnwidth]{CostTrends.png}}
\put(5.3,1.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.6){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.2,5.2){\shortstack[c]{Weighted sum:\\ $\mathbf{J}=J_P+cJ_S$}}
%\put(4.98,0.78){\circle*{0.1}}
%\put(2.48,1.57){\circle*{0.1}}
\put(5.00,0.81){\circle*{0.1}}
\put(2.47,1.60){\circle*{0.1}}
\put(4.8,-0.4){$K_{M-JPDAF}$}
\put(2.3,-0.4){$K_{C-JPDAF}$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to an element of an estimator gain $K$ (dashed: uncertainty cost $J_P$, dash-dot: similarity cost $J_S$, solid: weighted sum). The estimator gain $K_{M-JPDAF}$ is selected to minimize the uncertainty cost. The estimator gain $K_{C-JPDAF}$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association during close proximity tracking scenarios or missions.}
\label{fig:CostTrends}
\end{figure}

@@

%For each following scenario, several cases are simulated where various parameters are slightly changed with $\epsilon\in\Re$, summarized in Table \ref{tab:CaseDef}, and measurement are simulated with \refeqn{NonLin2BP} and \refeqn{zj}.
In the following scenarios, several cases are simulated with \refeqn{NonLin2BP} and measurements are generated according to \refeqn{zj}, but the measurement origins are not given to the data association algorithm.
Additionally, there is a $10\%$ chance that a measurement is either deleted or an extraneous measurement is added at each time step.
Since this probability is relatively small, the association probabilities are computed with \refeqn{betaDef} using $B=0$.
Further descriptions of the cases are available below, and the resulting accuracy over $n$ time steps is measured with RMS position (kilometers) and angular (radian) errors, defined as
\begin{align}
% MATLAB: RMS_r_indiv(k) = (sum((Ri{k}-Rhati{k}).^2)/NumStates).^0.5;
\mathbf{e}_{RMS,r,i}=\sqrt{\frac{\sum_{k=1}^n(r_{i,k}-\hat r_{i,k})^2}{n}}
, \quad
\mathbf{e}_{RMS,\theta,i}=\sqrt{\frac{\sum_{k=1}^n(\cos^{-1}(r_{i,k}^T\hat r_{i,k}))^2}{n}}
,
\end{align}
respectively, and the subsequent tabulated RMS errors are averaged over all objects. The uncertainty is summarized with $\tr{J_P}$, and the computation time is measured as well, tabulated in Tables \ref{tab:I}--\ref{tab:IV}.
Scenarios I and II are data association and filtering examples in LEO, while scenarios III and IV are GEO examples.
For readers with interest in how the algorithms handle perturbations, various parameters are slightly changed, tabulated at each scenario description.
The metrics from the perturbed cases are summarized in the subsequent tables as well.

@@

Various cases in LEO are simulated to compare the data association and filtering algorithms, namely the JPDAF, M-JPDAF, and C-JPDAF.
The process covariance is $Q=\diag[\sigma^2_rI_{3\times3},\dot\sigma^2_rI_{3\times3}]=\diag[10^{-6}I_{3\times3}\ \text{km}^2, 10^{-8}I_{3\times3}\ \text{km/s}^2]$ and the measurement uncertainty is $R=\diag[\sigma_\rho^2, \sigma_{\dot\rho}^2, \sigma_\alpha^2, \sigma_\delta^2]=\diag[(0.15\ \text{km})^2, (0.005\ \text{km/s})^2,\\ (\frac{0.01\pi}{180}\ \text{rad})^2, (\frac{0.01\pi}{180}\ \text{rad})^2]\in\Re^{4\times4}$ where these standard deviations are selected from the Mahe Ground Station uncertainty data~\cite{VerSauSco04} and~\cite{KurAriAriEfe10}.

@@

These cases serve to compare the JPDAF with the M-JPDAF for tracking two nearby satellites passing over the sensor field of view in GEO, where the orbital radius is $r_{GEO}=4.2164\times10^{4}\ \text{km}$. The initial conditions of the first two orbits are chosen as
\begin{align*}
x_{1,\text{III}}&=\begin{bmatrix}r_{GEO}, & 0\ \text{km}, & 0\ \text{km}, & 0\ \text{km/s}, & \sqrt{\frac{\mu}{r_{GEO}}}, & 0\ \text{km/s}\end{bmatrix}^T,
\\
x_{2,\text{III}}&=x_{1,\text{III}}+\begin{bmatrix}
0\ \text{km}, & 0\ \text{km}, & -1\ \text{km}, & 0\ \text{km/s}, & 0\ \text{km/s}, & 4\times10^{-4}\ \text{km/s}
\end{bmatrix}^T,
\end{align*}
or where $x_{1,\text{III}}$ remains exactly in GEO while $x_{2,\text{III}}$ starts slightly perturbed from a GEO orbit with a nonzero inclination such that the two satellites nearly collide as they pass by in close proximity.
The perturbations are summarized in Table \ref{tab:PertCaseIII}.
\begin{table}
\begin{center}
\caption{Perturbations for Scenario III Cases} \label{tab:PertCaseIII}
\begin{threeparttable}[h]
\begin{tabularx}{.75\textwidth}
{
>{$}c<{$} |
>{$}c<{$}
}
\toprule
\multirow{2}{*}{Perturbed Case} & \multirow{2}{*}{Perturbation}\\
\\
\midrule
\multirow{1}{*}{III.a} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-6}\text{ km}^2$}
\\
\multirow{1}{*}{III.b} &  \multirow{1}{*}{$\sigma^2_{\dot r} = 1.1\times10^{-8}(\text{ km/s})^2$}
\\
\multirow{1}{*}{III.c} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-6}\text{ km}^2$, $\sigma^2_{\dot r} = 1.1\times10^{-8}(\text{ km/s})^2$}
\\
\multirow{1}{*}{III.d} &  \multirow{1}{*}{$\sigma^2_{\alpha} = \sigma^2_{\delta} = 3.3508\times10^{-8}\text{ rad}^2$}
\\
\bottomrule
\end{tabularx}
\end{threeparttable}
\end{center}
\end{table}
The III cases consider small initial covariance matrices $P_{0,\text{III}}= Q$ where $Q$ is defined the same as the LEO cases for time steps of $10$ seconds over $5000$ seconds.
%These scenarios are chosen because the estimates exhibit large initial uncertainties, so the spread in the innovations affects the updates.
Even though the initial conditions are largely different from those of the I cases, the III cases display the same trends, where the computational costs among the algorithms are roughly the same but the tracking abilities of the M-JPDAF \emph{always} yield estimates closer to the truth with less uncertainty than those of the JPDAF.
These results are tabulated in Table \ref{tab:III}, and some cases are plotted in Figure \ref{fig:III}.

@@

The JPDAF, M-JPDAF, and C-JPDAF algorithms are compared for two satellites in GEO with initial conditions
\begin{align}
\begin{split}
x_{1,\text{IV}}&=f_{GEO}(0^\circ), \quad x_{2,\text{IV}}=f_{GEO}({10^{-4}}^\circ), \quad \mbox{where}
\\
f_{GEO}(\theta)&=r_{GEO}\begin{bmatrix}\cos\theta, & \sin\theta, & 0, & -\sqrt{\frac{\mu}{r_{GEO}^3}}\sin\theta, & \sqrt{\frac{\mu}{r_{GEO}^3}}\cos\theta, & 0\end{bmatrix}^T,
\end{split}
\end{align}
where $Q=\diag[\sigma^2_rI_{3\times3}, \dot\sigma^2_rI_{3\times3}]=\diag[10^{-8}I_{3\times3}\ \text{km}^2, 10^{-10}I_{3\times3}\ \text{km/s}^2]$.
The perturbations are summarized in Table \ref{tab:PertCaseIV}.
\begin{table}
\begin{center}
\caption{Perturbations for Scenario IV Cases} \label{tab:PertCaseIV}
\begin{threeparttable}[h]
\begin{tabularx}{.75\textwidth}
{
>{$}c<{$} |
>{$}c<{$}
}
\toprule
\multirow{2}{*}{Perturbed Case} & \multirow{2}{*}{Perturbation}\\
\\
\midrule
\multirow{1}{*}{IV.a} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-8}\text{ km}^2$}
\\
\multirow{1}{*}{IV.b} &  \multirow{1}{*}{$\sigma^2_{\dot r} = 1.1\times10^{-10}(\text{ km/s})^2$}
\\
\multirow{1}{*}{IV.c} &  \multirow{1}{*}{$\sigma^2_{r} = 1.1\times10^{-6}\text{ km}^2$, $\sigma^2_{\dot r} = 1.1\times10^{-8}(\text{ km/s})^2$}
\\
\multirow{1}{*}{IV.d} &  \multirow{1}{*}{$\sigma^2_{\alpha} = \sigma^2_{\delta} = 3.3508\times10^{-8}\text{ rad}^2$}
\\
\bottomrule
\end{tabularx}
\end{threeparttable}
\end{center}
\end{table}
The initial state covariance is $P_{0,\text{IV}}=Q$, where the time steps are $10$ seconds over a $2000$ second time period.
This corresponds to a scenario where two satellites orbit steadily nearby in GEO.
For the C-JPDAF, the parameters $a=1.5\times10^{2}$ and $c=1\times10^{10}$ from \refeqn{zetaGeneral} and \refeqn{CostGen} are used in these scenarios from trial and error.
In theory, topocentric right ascension measurements should be the same distance apart throughout the cases and the declination should always be zero.
Much like the II cases, the accuracy of the C-JPDAF yields a large improvement from that of the JPDAF and M-JPDAF; however, the increase in computational cost of the C-JPDAF is roughly $30$ times that of either other algorithm, which is about half of the increase found with the II cases.
This is because the similarity measure is less complex with the IV cases than with the II cases due to the number of estimates and the size of the measurement space.
The angular RMS errors and computation times are tabulated in Table \ref{tab:IV} and some example plots from these cases are shown in Figure \ref{fig:IV}. In applications with a large number of objects to track, the C-JPDAF need not be applied on most objects; only those close neighbors where the similarity among the estimates yield coalescence with the JPDAF or the M-JPDAF. This way, a data association scheme with an analytic solution, such as the JPDAF or the M-JPDAF, could be applied to the remaining estimates to mitigate the large computational requirements of the C-JPDAF.

### 2018-06-09 Journal/JAS Data Association/JAS_DataAssoc copy.tex
journal added

Let $G_{ij}\in\Re$ be a scaled density function used repeatedly between the $i$-th measurement estimate and the $j$-th measurement, defined as
% variable which takes a very similar form as the Gaussian probability density function
\begin{align}
G_{ij}=\frac1{\sqrt{\det{S_{i}}}}\exp{\{-\frac12e_{ij}^TS_{i}^{-1}e_{ij}\}}.
\end{align}
%This is used to calculate intermediate variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$
%\begin{align}
%\mathcal{S}_{ti}=\sum\limits_{j\in J}G_{ij}, 
%\quad 
%\mathcal{S}_{ri}=\sum\limits_{i\in I}G_{ij}.
%\end{align}
Then, a close approximation of the probability that the $i$-th system is associated with the $j$-th measurement is (from~\cite{Bar1990})
\begin{align}
\label{eqn:betaDef}
\beta_{ij}=\frac{G_{ij}}{\sum\limits_{l=1}^{n_r}G_{il}+\sum\limits_{l=1}^{n_t}G_{lj}-G_{ij}+B},
\end{align}
where $B$ accounts for measurements \emph{not} originating from known targets. When $B=0$, this corresponds to rare extraneous measurements and missed detections. When these are prevalent, tuning $B$ is required, though this is beyond the paper scope.

%When these are prevalent, a fixed value of $B$ in \refeqn{betaDef} was found from simulations to provide a close approximation of $\beta_{ij}$ in various applications, though tuning this parameter is beyond the scope of this paper.

%In this paper, we assume that at most a single measurement may originate from a single object, and missed detections and measurements originating from extraneous clutter are considered insignificant, so $B=0$ is used to determine joint association probability.

%this approximation is valid when extraneous measurements and missed detections are rare. Even if missed detections and measurements originating from extraneous clutter is present, \refeqn{betaDef} performs well~\cite{Bar1990}.

%\EditTL{(The above writing has several issues that the reviewers of ACC15 mentioned. (i) There is no indication on the dimension of variables. For example is $G_{ij}$ a scalar or a vector; (ii) there are several variables, such as $e_{ij}$ or $S_i$ that were used before defining them explicitly. Saying that it is the innovation and the a priori innovation covariance is not sufficient. Ideally, we have to define a variable before using it; (iii) The definition of $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$ is unclear. Is $t$ also an indexed variable?; (iv) Do you really have to introduce the set $I$ and $J$. It is causing more confusion as several other variations of $J$ will appear later in this paper. Would it be more concise to rewrite it as $\sum_{j=1}^{n_r}$?; (v) Do we really have to introduce the variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$. If they are used here only, there is no need to define them. It's better to substitute (6) into (7). Usually, a new variable or symbol is defined, only if it has an important meaning, or it is used repeatedly later; (vi) how is $B$ defined, and what's the dimension of it. Give the explicit definition, or at least cite something. The given explanation raises more questions. }

@@

%For each following scenario, several cases are simulated where various parameters are slightly changed with $\epsilon\in\Re$, summarized in Table \ref{tab:CaseDef}, and measurement are simulated with \refeqn{NonLin2BP} and \refeqn{zj}.
In the following scenarios, several cases are simulated with \refeqn{NonLin2BP} and measurements are generated according to \refeqn{zj}, but the measurement origins are not given to the data association algorithm.
Additionally, there is a $10\%$ chance that a measurement is either deleted or an extraneous measurement is added at each time step.
Since this probability is relatively small, the association probabilities are computed with \refeqn{betaDef} using $B=0$.
Further descriptions of the cases are available below, and the resulting accuracy over $n$ time steps is measured with RMS position (kilometers) and angular (radian) errors, defined as
\begin{align}
% MATLAB: RMS_r_indiv(k) = (sum((Ri{k}-Rhati{k}).^2)/NumStates).^0.5;
\mathbf{e}_{RMS,r,i}=\sqrt{\frac{\sum_{k=1}^n\norm{r_{i,k}-\hat r_{i,k}}^2}{n}}
, \quad
\mathbf{e}_{RMS,\theta,i}=\sqrt{\frac{\sum_{k=1}^n(\cos^{-1}(r_{i,k}^T\hat r_{i,k}))^2}{n}}
,
\end{align}
respectively, and the subsequent tabulated RMS errors are averaged over all objects. The uncertainty is summarized with $\tr{J_P}$, and the computation time is measured as well, tabulated in Tables \ref{tab:I}--\ref{tab:IV}.
Scenarios I and II are data association and filtering examples in LEO, while scenarios III and IV are GEO examples.
For readers with interest in how the algorithms handle perturbations, various parameters are slightly changed, tabulated at each scenario description.
The metrics from the perturbed cases are summarized in the subsequent tables as well.

>>>>

Let $G_{ij}\in\Re$ be a scaled density function used repeatedly between the $i$-th measurement estimate and the $j$-th measurement, defined as
% variable which takes a very similar form as the Gaussian probability density function
\begin{align}
G_{ij}=\frac1{\sqrt{\det{S_{i}}}}\exp{\{-\frac12e_{ij}^TS_{i}^{-1}e_{ij}\}}.
\end{align}
%This is used to calculate intermediate variables $\mathcal{S}_{ti}$ and $\mathcal{S}_{ri}$
%\begin{align}
%\mathcal{S}_{ti}=\sum\limits_{j\in J}G_{ij}, 
%\quad 
%\mathcal{S}_{ri}=\sum\limits_{i\in I}G_{ij}.
%\end{align}
%
%
%Then, a close approximation of the probability that the $i$-th system is associated with the $j$-th measurement is (from~\cite{Bar1990})
%\begin{align}
%\label{eqn:betaDef}
%\beta_{ij}=\frac{G_{ij}}{\sum\limits_{l=1}^{n_r}G_{il}+\sum\limits_{l=1}^{n_t}G_{lj}-G_{ij}+B},
%\end{align}
%where $B$ accounts for measurements \emph{not} originating from known targets. When $B=0$, this corresponds to rare extraneous measurements and missed detections. When these are prevalent, tuning $B$ is required, though this is beyond the paper scope.
Then, a close approximation of the probability that the $i$-th system is associated with the $j$-th measurement is adopted from~\cite{Bar1990} as
\begin{align}
\label{eqn:betaDef}
\beta_{ij}=\frac{G_{ij}}{\sum\limits_{l=1}^{n_r}G_{il}+\sum\limits_{l=1}^{n_t}G_{lj}-G_{ij}+B},
\end{align}
where $B\geq0$ is the variable that accounts for measurements \emph{not} originating from known targets. When $B=0$, this corresponds to rare extraneous measurements and missed detections. 
When these are prevalent, a fixed value of $B$ in \refeqn{betaDef} was found from simulations by tuning to provide a close approximation of $\beta_{ij}$.% in various applications.

@@

%For each following scenario, several cases are simulated where various parameters are slightly changed with $\epsilon\in\Re$, summarized in Table \ref{tab:CaseDef}, and measurement are simulated with \refeqn{NonLin2BP} and \refeqn{zj}.
In the following scenarios, several cases are simulated with \refeqn{NonLin2BP} and measurements are generated according to \refeqn{zj}, but the measurement origins are not given to the data association algorithm.
Additionally, there is a $10\%$ chance that a measurement is either deleted or an extraneous measurement is added at each time step.
Since this probability is relatively small, the association probabilities are computed with \refeqn{betaDef} using $B=0$.
Further descriptions of the cases are available below, and the resulting accuracy over $n$ time steps is measured with RMS position (kilometers) and angular (radian) errors, defined as
\begin{align}
% MATLAB: RMS_r_indiv(k) = (sum((Ri{k}-Rhati{k}).^2)/NumStates).^0.5;
\mathbf{e}_{RMS,r,i}=\sqrt{\frac{\sum_{k=1}^n\norm{r_{i,k}-\hat r_{i,k}}^2}{n}}
, \quad
\mathbf{e}_{RMS,\theta,i}=\sqrt{\frac{\sum_{k=1}^n(\cos^{-1}(r_{i,k}^T\hat r_{i,k}))^2}{n}}
,
\end{align}
respectively, and the subsequent tabulated RMS errors are averaged over all objects. 
The position RMS error metrics are decomposed into range and direction components because range measurements are available in LEO cases and angles-only measurements are available in GEO cases.
The uncertainty is summarized with $\tr{J_P}$, and the computation time is measured as well, tabulated in Tables \ref{tab:I}--\ref{tab:IV}.
Scenarios I and II are data association and filtering examples in LEO, while scenarios III and IV are GEO examples.
For readers with interest in how the algorithms handle perturbations, various parameters are slightly changed, tabulated at each scenario description.
The metrics from the perturbed cases are summarized in the subsequent tables as well.
